rotation_runs2019

### 2019-10-02 inst/documents/rotation_runs2019.Rmd
corrected bugs in rotation_runs2019.Rmd to do with saving rot_interval

  # to compare sequence to rotation run all the scenarios above for both seq & rot 
  for(rot_or_not in 0:1)
  {  
    #to get rot_int of 0 in alternate runs - the other run uses the value from the input file
    if (rot_or_not == 0) linputs$rot_interval <- 0

@@

  # if the first scenario create df to store results of all scenarios
  if (i==1)
  {
    df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=n_scenarios))
    names(df_res_all) <- names(df_in_out)
  }

@@

>>>>

  if (linputs$rot_interval == 0) stop("in rotation_runs2019 rot_interval in input file needs to be > 0 to allow it to be compared to a sequence")

  #record rotation rot interval locally otherwise it get soverwritten by 0
  rot_rot_interval <- linputs$rot_interval

  # to compare sequence to rotation run all the scenarios above for both seq & rot 
  # need to do the rotation 2nd so that rot_interval from the input file can be saved with the outputs
  for(rot_or_not in 0:1)
  {  
    #to get rot_int of 0 in alternate runs - the other run uses the value from the input file
    if (rot_or_not == 0) linputs$rot_interval <- 0
    else linputs$rot_interval <- rot_rot_interval

@@

  # if the first scenario create df to store results of all scenarios
  if (i==1)
  {
    df_res_all <- data.frame(matrix(NA, ncol=length(names(df_in_out)), nrow=nscenarios))
    names(df_res_all) <- names(df_in_out)
  }

@@

  #can save partial outputs in case doesn't make to end
  if (i==nscenarios | i%%1000 == 0)
  {

    # save object containing inputs and results as rda for analysis
    # by default saved to inst/documents folder
    save(df_res_all, file='df_res_all_rot.rda') #paste0(outFolder,'*.rda'))    
  }
